\section{Experimental Results}
\subsection{Part 1: Hopper}
The Part 1 implementation produced learning-curve plots for REINFORCE without baseline, REINFORCE with a constant baseline of 20, and the actor-critic variant. The plots show that all three runs can eventually reach high returns, but the learning curves are noisy and single-seed only. The constant baseline improves the early REINFORCE curve relative to the no-baseline run, but it does not remove instability. The actor-critic run uses a learned value baseline and reaches high return near the end of training, although it also exhibits long low-return phases.

\begin{table}[H]
\centering
\small
\begin{tabular}{p{0.34\linewidth}ccc}
\toprule
Method & Seed & Episodes & Final metric \\
\midrule
REINFORCE & 0 & 3000 & \TODO{eval} \\
REINFORCE, $b=20$ & 0 & 3000 & \TODO{eval} \\
Actor-critic & 0 & 3000 & \TODO{eval} \\
\bottomrule
\end{tabular}
\caption{Part 1 runs currently available as plots in \texttt{part1/plots/}. The final report should fill this table with deterministic evaluation means and standard deviations, preferably over at least three seeds.}
\label{tab:hopper-results}
\end{table}

\subsection{Part 2: Training Diagnostics}
SAC was selected as the main Part 2 algorithm because the available logs show faster and more reliable success than PPO. The clearest SAC runs reach high training success after 500k steps. PPO logs are more variable: some runs remain near 0.15--0.19 success even after many updates, while one run reaches 0.87 around 2M steps. This is consistent with the expected advantage of off-policy SAC on goal-conditioned manipulation, especially when replay and optional HER are available.

\begin{table}[H]
\centering
\small
\begin{tabular}{lcc}
\toprule
Run & Step & Train SR \\
\midrule
SAC none source & 499700 & 0.97 \\
SAC none target & 499933 & 1.00 \\
SAC UDR source & 499988 & 0.99 \\
SAC UDR + friction & 499957 & 0.96 \\
Best logged PPO run & 2015232 & 0.87 \\
\bottomrule
\end{tabular}
\caption{Final TensorBoard training success rates from available logs. These are training diagnostics, not a substitute for the deterministic evaluation table.}
\label{tab:training-diagnostics}
\end{table}

\subsection{Nominal Sim-to-Sim Evaluation}
Table~\ref{tab:nominal-eval} reports deterministic 50-episode evaluations generated from the saved SAC checkpoints. At the nominal target mass of 5 kg, the source-trained SAC policy already transfers well: the gap between source$\rightarrow$source and source$\rightarrow$target is small in success rate. The target-trained model is still the oracle upper bound.

\begin{table*}[t]
\centering
\small
\begin{tabular}{llcccc}
\toprule
Model & Evaluation & Mean return & Std return & Success & Mass \\
\midrule
SAC none source & source & -1.536 & 7.574 & 98\% & 1 kg \\
SAC none source & target & -2.316 & 9.578 & 96\% & 5 kg \\
SAC none target & target & -0.429 & 0.274 & 100\% & 5 kg \\
SAC UDR + friction source & source & -9.761 & 46.666 & 94\% & 1 kg \\
SAC UDR + friction source & target & -6.509 & 26.756 & 94\% & 5 kg \\
\bottomrule
\end{tabular}
\caption{Available 50-episode deterministic SAC evaluations with fixed nominal mass and fixed nominal friction, seed 42. The UDR checkpoint is the saved \texttt{SAC\_udr\_source\_500k\_friction} model.}
\label{tab:nominal-eval}
\end{table*}

\subsection{Harder Mass and Friction Evaluation}
Because nominal mass transfer was already strong, the evaluation was extended to randomize parameters at test time. Table~\ref{tab:hard-eval} uses mass sampled uniformly in $[5,10]$ kg, object/table lateral friction sampled in $[0.2,1.5]$, and object spinning friction sampled in $[0,0.01]$. Under this harder protocol, the non-randomized source policy drops from 96\% to 76\% success on target. The UDR policy trained with mass and friction randomization reaches 90\%, suggesting that UDR is more useful when the evaluation distribution is wider than the original source-target mass shift.

\begin{table}[H]
\centering
\small
\begin{tabular}{lccc}
\toprule
Model & Mean return & Std & Success \\
\midrule
SAC none source & -10.990 & 17.411 & 76\% \\
SAC UDR + friction & -5.004 & 14.170 & 90\% \\
\bottomrule
\end{tabular}
\caption{Hard target evaluation over 50 deterministic episodes, seed 42. The sampled masses had min 5.219 kg, mean 7.676 kg, and max 9.878 kg.}
\label{tab:hard-eval}
\end{table}

\subsection{Missing Final Experiments}
The following results are still required before the report can be considered final: PPO deterministic evaluation with valid normalization statistics, ADR source$\rightarrow$source and source$\rightarrow$target evaluation, multi-seed means and standard deviations, and the final Part 1 numeric table. \TODO{Run the mandatory final grid and replace the TODO cells before submission.}
