\section{Discussion}
\subsection{Result Analysis}
The most important observation is that the nominal source to target transfer is easier than expected from mass alone. A source-trained SAC policy reaches 97.3\% success on the 5 kg target object, only slightly below its 99.3\% source success. This suggests that the current \texttt{PandaPush-v3} setup is not negatively influenced by the fixed 1  to 5 kg mass shift. The task has a fixed goal, a short object-goal distance distribution, dense rewards during training, and a powerful continuous-control algorithm. These factors can hide part of the intended reality gap.
The harder setting was introduced to obtain results that are more meaningful and applicable to real-world scenarios
When target mass is sampled in $[5,10]$ kg and friction is randomized, the non-randomized SAC policy falls to 72.0\% success. This indicates that friction and heavier masses expose failures that are not visible in the nominal target evaluation.
Observing the result of the training, SAC has better performance compared to PPO.The experiments show that SAC achieves training success after 500k steps, while PPO runs are less consistent. This is coherent with the algorithms: SAC is off-policy and can reuse data through its replay buffer, whereas PPO is on-policy and discards rollouts after each update. For goal-conditioned pushing, replay-based learning is especially useful because informative transitions can be reused many times.

\subsection{Why ADR Outperforms UDR Trained on the Target Distribution}

The most counter-intuitive result is that the ADR source model (94.0\%) outperforms the UDR hard target model (85.3\%) despite the latter being trained on a distribution that exactly matches the evaluation distribution.
A natural first hypothesis is that certain combinations of mass and friction are physically beyond the arm's capability: the Panda joints have limited torques (87~N on most joints), and pushing a 10~kg object against high friction may be infeasible regardless of the policy.
Where is the gap coming from if both models are trained in the same environment?
If some physics configurations were impossible, the ADR model would fail on them too, and the success rates would converge.
Since ADR reaches 94\%, the arm is capable of solving nearly all the sampled configurations; the UDR model simply has not learned how.

The more likely explanation is a curriculum effect.
UDR exposes the policy to the full difficulty range from the very first episode of training.
With only 500k steps and 100k warm-up steps in the replay buffer, the policy has roughly 400k gradient updates to learn a single robust strategy covering the entire $[5,10]$~kg $\times\,[0.2,1.5]$ friction space simultaneously.
The per-friction-bin breakdown (Table~\ref{tab:udr-friction-bins}) shows that the UDR policy performs well at the lowest friction values and degrades at higher ones, but the mass bins do not follow a clean monotonic pattern (success is non-monotonic across the $[5,10]$~kg range).
With only 50 evaluation episodes, the per-bin sample counts are too small (6--13 episodes) to conclude that the policy systematically biased toward any particular region of the parameter space.
The most robust conclusion is that the UDR policy shows high variance and inconsistent generalization across the joint mass--friction space, consistent with insufficient training under a wide uniform distribution.

ADR avoids this failure mode by construction.
Starting from the nominal source dynamics, the curriculum expands the training range only when the current policy achieves a success rate above 70\%.
The policy is therefore never overwhelmed: it first masters easy pushes, then incrementally adapts to heavier and more friction-variable objects.
By the time the curriculum reaches the hard end of the range, the policy already has a strong behavioral prior that it refines rather than learns from scratch.

This result suggests that, under a fixed compute budget, a well-designed curriculum is more data-efficient than training on the target distribution directly.
It also motivates exploring ADR with friction as a first-class curriculum axis rather than expanding mass and friction simultaneously from a single success signal.

\subsection{Reward Shaping}
The reward-shaping wrapper affects training but not the evaluation success metric. The time penalty encourages short solutions, and the close-goal bonus increases the learning signal once the object reaches the success threshold. For SAC, this can increase success rate indirectly by making successful behavior easier to learn early in training. However, it also makes training return less comparable to raw evaluation return. This is why the evaluation script reports both return and success rate on the unwrapped environment.

\subsection{Methodological Critique}
The main limitation is that the current result set is not yet statistically complete. Most numbers are single-seed evaluations with 50 episodes. They are useful for debugging and for identifying trends, but the final report should include mean and standard deviation across seeds where possible.

The domain-randomization implementation is also intentionally simple. UDR uses hand-selected uniform ranges, so its behavior depends strongly on those ranges. If the training range matches the evaluation range too closely, the comparison becomes too generous. The current setup avoids the most direct form of this issue by using conservative training friction ranges and a harder evaluation range, but a final study should report the exact train and test distributions clearly.

ADR is currently mass-only and uses a simple success-rate heuristic. It does not adapt friction, center of mass, action noise, observation noise, or target sampling. Therefore, any ADR result should be interpreted as a curriculum over object mass rather than as a full automatic domain-randomization method. In addition, the source-domain success rate may be a weak curriculum signal for transfer: a policy can be successful in the randomized training domain while still failing on the target distribution.

Finally, PPO evaluation needs care because some saved PPO models were trained behind \texttt{VecNormalize}. A valid deterministic PPO evaluation must load the corresponding normalization statistics; otherwise the policy sees observations on a scale different from training. This is marked as TODO instead of reporting unreliable numbers.
